GSEA datasets for FDR benchmarking

### 2017-11-08 datasets/GSEA/gsea.Rmd
Added supplementary option to plots. Added plotFDRMethodsOverlap.

```{r runningBenckmark, message=FALSE}
designBen <- initializeBenchDesign()
res <- dplyr:::select( goRes, c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
res$pval <- pmin( res$pval, 1 )
head(res)
sGSEA <- designBen %>% buildBench( res, ftCols="ind_covariate")
elementMetadata( rowData(sGSEA) )
assayNames(sGSEA) <- "qvalue"
sGSEA <- addDefaultMetrics( sGSEA )
```

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=FALSE )

stopifnot( all(assays(sGSEA)[["qvalue"]][,"unadjusted"] == pmin(goRes$over_represented_pvalue, 1) ) )

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)
rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=TRUE )

>>>>

```{r runningBenckmark, message=FALSE}
designBen <- initializeBenchDesign()
res <- dplyr:::select( goRes, c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
res$pval <- pmin( res$pval, 1 )
sGSEA <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(sGSEA) <- "qvalue"
sGSEA <- addDefaultMetrics( sGSEA )
```

```{r plottingResults}
rejections_scatter( sGSEA, as_fraction=TRUE, supplementary=FALSE)

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)
rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=TRUE, supplementary=FALSE)
```

```{r}

plotFDRMethodsOverlap( sGSEA, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
